A Switching Planner for Combined Task and Observation Planning

### 2011-02-05 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
6.5 pages

More generally, there has been much recent work on scaling POMDP
solution procedures to medium-sized
instances~\cite{shani:etal:08,KurHsu08}. In that
setting \citeauthor{kurniawati:etal:2010}~(\citeyear{kurniawati:etal:2010})
recently addressed an inefficiency of offline point-based techniques
in problems with medium length planning horizons, however their
approach take tens of minutes to good plans, and only scales to tens
of thousands of states. In the case of general domain-independent
factored systems, the state-of-the-art scales to relatively small
problems with $2^{22}$ states~\cite{shani:etal:2008}. At their limit,
these procedures take over an hour to converge, and $\sim10$ seconds
on average to perform a single Bellman backup.  For classes of POMDP
that feature exploitable structures (e.g., no actions with negative
effects), problems with as many as $10^{30}$ states can be targeted by
offline procedures~\cite{brunskill:russell:2010}. Moving someway
towards addressing real-time decision making, recent online POMDP
solution procedures have been developed which can exploit highly
approximate value functions -- typically computed using a point-based
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. Their applicability in our setting is
limited, firstly because they only scale to smaller problems, with
thousands of states, and also due to the large amount of
\emph{problem-specific} offline processing that might be required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

@@

Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
---i.e., sequential planning in unobservable worlds--- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. Most
recently this research thread has been extended to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.
%%
The continual planning system that motivated our
project~\cite{brenner:nebel:jaamas09} also has this characteristic,
and has been applied in completely observable domains, particularly
those featuring multiple communicating agents.

>>>>

More generally, there has been much recent work on scaling POMDP
solution procedures to medium-sized
instances~\cite{shani:etal:08,KurHsu08}. In that
setting \citeauthor{kurniawati:etal:2010}~(\citeyear{kurniawati:etal:2010})
recently addressed an inefficiency of offline point-based techniques
in problems with medium length planning horizons, however their
approach take tens of minutes to good plans, and only scales to tens
of thousands of states. In the case of general domain-independent
factored systems, the state-of-the-art scales to relatively small
problems with $2^{22}$ states~\cite{shani:etal:2008}. At their limit,
these procedures take over an hour to converge, and $\sim10$ seconds
on average to perform a single Bellman backup.  For classes of POMDP
that feature exploitable structures (e.g., no actions with negative
effects), problems with as many as $10^{30}$ states can be targeted by
such offline procedures~\cite{brunskill:russell:2010}. Moving someway
towards addressing real-time decision making, recent online POMDP
solution procedures have been developed which can exploit highly
approximate value functions -- typically computed using a point-based
procedure -- and heuristics in forward
search~\cite{ross:etal:2008}. Their applicability in our setting is
limited, firstly because they only scale to smaller problems, with
thousands of states, and also due to the large amount of
\emph{problem-specific} offline processing that might be required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

@@

Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
---i.e., sequential planning in unobservable worlds--- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. Most
recently this research thread has been extended to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.
%%
%% The continual planning system that motivated our
%% project~\cite{brenner:nebel:jaamas09} also has this characteristic,
%% and has been applied in completely observable domains, particularly
%% those featuring multiple communicating agents.
